### 2021-05-18 chatbot_classification/03.emnlp_2021/experiments.tex
modified:   experiments.tex   modified:   methodology.tex

\subsection{Datasets}
Our experiments aim to study the short text classification in the low-resource environment popular in the task-specific conversational chatbot application.
The datasets adopted in our experiments, showed in \ref{tbe:dataset statistic} \footnote{All settings of six public datasets would be released to github soon.}, typically contain comparatively large number of class labels, ranging from several dozens to hundreds, and each class label is associated with a handful of labeled queries with each query being usually one sentence.

@@

Our SFC implementations include three 2-stage SFCs using task 1 and 2 with ablation in Table \ref{tbe:table2}; one joint-SFC trained on all three tasks in Table \ref{tbe:table2}; one joint-SFC with an additional fourth NER task in Table \ref{tbe:addtional ner experiments}.

@@

\subsubsection*{Multi-task and joint training} 
\begin{table}
  \begin{centering}
    \scalebox{0.65}{
      \begin{tabular}{|c|ccc|ccc|}
        \hline
        \multicolumn{1}{|c|}{\multirow{2}*{\textbf{Models}} }& \multicolumn{3}{c|}{\textbf{FRAMES}}& \multicolumn{3}{c|}{\textbf{ATIS}}\tabularnewline
        \cline{2-7}
        \multicolumn{1}{|c|}{} & $\textbf{10}$ & $\textbf{20}$ & $\textbf{50}$
        & $\textbf{10}$ & $\textbf{20}$ & $\textbf{50}$\tabularnewline
        \hline
        RoBERTa-large & \multirow{2}*{${0.3456}$} & \multirow{2}*{${0.4043}$} & \multirow{2}*{${0.4262}$} & \multirow{2}*{${0.9349}$} & \multirow{2}*{${0.9757}$} & \multirow{2}*{${0.9800}$}\tabularnewline
        (classification) & & & & & & \tabularnewline
        \hline
        RoBERTa-large & \multirow{3}*{${0.3520}$} & \multirow{3}*{${0.4088}$} & \multirow{3}*{${0.4353}$} & \multirow{3}*{${0.9560}$} & \multirow{3}*{${0.9706}$} & \multirow{3}*{$\textbf{0.9832}$}\tabularnewline
        (classification & & & & & & \tabularnewline
        w/ NER) & & & & & & \tabularnewline
        \hline
        Joint-SFC & \multirow{2}*{${0.3843}$} &
        \multirow{2}*{${0.4130}$} & \multirow{2}*{${0.4390}$} &
        \multirow{2}*{${0.9618}$} & \multirow{2}*{${0.9761}$} & 
        \multirow{2}*{${0.9825}$}\tabularnewline
        (w/o NER) & & & & & & \tabularnewline
        \hline
        Joint-SFC & \multirow{2}*{$\textbf{0.3925}$} &
        \multirow{2}*{$\textbf{0.4420}$} & \multirow{2}*{$\textbf{0.4456}$} &
        \multirow{2}*{$\textbf{0.9639}$} & \multirow{2}*{$\textbf{0.9784}$} & 
        \multirow{2}*{${0.9826}$}\tabularnewline
        (w/ NER) & & & & & & \tabularnewline
        \hline
      \end{tabular}
    }
  \end{centering}

@@

\begin{table}
  \begin{centering}
    \scalebox{0.85}{
      \begin{tabular}{|c|c|c|c|}
        \hline
        F1 score & 2-stage SFC & joint-SFC & Gap \tabularnewline
        \hline
        top-1 accuracy & \textbf{81.50} & 81.07 & -0.47 \tabularnewline
        top-5 accuracy & 94.01 & \textbf{94.30} & +0.29 \tabularnewline
        \hline
      \end{tabular}
    }
    \par
  \end{centering}
  \caption{The average classification accuracy in percentage in stage 1 on all five dataset.}
  \label{tbe:top1_5_accuracy}
\end{table}

@@

Joint-SFC consistently outperforms 2-stage SFC with multi-task training on 5 diverse datasets by 0.95 percentage point on average. 
Though a joint model structure may bring extra complexity to the system, it does alleviate the error propagation from the first stage and improves the final performance.

In following analysis, we will focus on the comparison between joint-SFC and the other baseline models.

\subsubsection*{Fusion of classification and similarity models} 
%We compare joint-SFC with classification, similarity and NER joint model based baselines respectively.

\begin{table}
  \begin{centering}
    \scalebox{0.58}{
      \begin{tabular}{|c|c|c|c|c|c|c|}
        \hline 
        \multicolumn{1}{|c|}{\multirow{2}*{Dataset}}&\multicolumn{1}{c|}{\multirow{2}*{Model}}& $K=3$ & $K=5$ & $K=10$ & $K=15$ & $K=20$\tabularnewline
        \multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & $P=20$ & $P=10$ & $P=5$ & $P=4$ & $P=3$\tabularnewline
        \hline
        \multicolumn{1}{|c|}{\multirow{2}*{ITG}}& 2-stage SFC & $0.8034$ & $0.8124$ & $0.8008$ & $0.7967$ & $0.7934$\tabularnewline
        \cline{2-7}
        \multicolumn{1}{|c|}{} & joint-SFC & $0.7986$ & $0.8114$ & $0.8010$ & $0.7972$ & $0.7918$\tabularnewline
        \hline
        \multicolumn{1}{|c|}{\multirow{2}*{Amazon-670k}}& 2-stage SFC & $0.7278$ & $0.7364$ & $0.7366$ & $0.7328$ & $0.7204$\tabularnewline
        \cline{2-7}
        \multicolumn{1}{|c|}{} & joint-SFC & $0.7334$ & $0.7445$ & $0.7516$ & $0.7344$ & $0.7373$\tabularnewline
        \hline
      \end{tabular}
      \par
    }
  \end{centering}
  \caption{
    We show the performances of SFC from different settings of hyperparameters, $K$ denoting the candidate class number from stage 1,
    $P$ denoting the number of sampled sentence pair in stage 2. 
  }
  \label{tbe:table3}
\end{table}

Regarding the classification models, joint-SFC outperforms RoBERTa-large based, the strongest among all baselines, by 2.04 percentage points on average F1 score over 5 datasets. 
Especially, ALBERT.xxlarge based is rather unstable in this short sentence task. 
Thus, we run multiple times with different settings and report the best ones here. 
Comparatively, RoBERTa based is the most stable and has the best performance almost all experiment settings.

Regarding the similarity model, as analyzed above, we only choose the RoBERTa-large based implementation as our baseline. 
Joint-SFC achieves more improvement of 7.09 percentage points on average F1 score. 
This is also understandable, since RoBERTa-large based similarity model does not and also can not train towards the task specific goal.

@@

\subsubsection*{Joint-SFC improves stage 1?}
We explore the quality of predicted candidate labels in stage 1 from 2-stage SFC and joint-SFC respectively. 
We should note that 2-stage SFC does not optimize the stage 1 model, namely a RoBERTa based classification model.

From Table \ref{tbe:top1_5_accuracy}, the joint training does not improve the top-1 classification accuracy in stage 1, yet it improves the top-5 accuracy.
The reason is that, a classification model inherently optimizes the objective loss, 0-1 error of top-1 here; the sentence pair similarity model in joint-SFC poses more positive effect in optimizing the candidate labels.

\subsubsection*{Supportive of extra NER loss}
Many previous work shows joint training with a NER loss improves the intent classification task as well, observed again in our baselines and SFCs in Table \ref{tbe:addtional ner experiments}.
We choose the state-of-the-art RoBERTa-large model with NER loss as a strong baseline.

We can see that our joint-SFC without NER loss still outperforms RoBERTa with NER loss baseline by 0.86 percentage points on average. 
This indicates that the fusion of classification and similarity models can even works better than fusing with additional NER information under few-shot chatbot scenario.

Moreover, the adding NER loss to joint-SFC further achieves improvement of 1.66 percentage points over RoBERTa with NER loss baseline. 
Especially on FRAMES dataset, which is a much more difficult task in comparison with ATIS based on performance of all systems on it, our joint-SFC with NER loss achieves a bigger improvement of 2.8 percentage points on average.

\subsubsection*{Different training sample size} 
We analyze the overall improvement trend of joint-SFC under various few-shot settings, and show results in Fig. \ref{fig:trend}.

Our main focus is on studying chatbot construction in real world applications, where each class has only a small number of example sentences.
The experimental results for the 3 diverse intent detection datasets (ClINC150, BANKING77, HWU64) under few-shot settings, 5 to 50 samples per class, indicate that our proposed joint-SFC can achieve average 2.47 percentage points improvement over one of the most powerful baseline models, which is RoBERTa-large classification model. 
Moreover, the improvement in F1 score becomes more and more prominent with the decrease of data sample number per class.

@@

Especially, in the most extreme setting with only 5 training samples per class, joint-SFC achieves 4.97 percentage points improvements on average over RoBERTa-large classification model. 
Joint SFC is a better choice applied into the early stage of building a task-specific chatbot system, since label data is extremely scarce.

@@

\subsubsection*{Relation to the label embedding based LEAM}
LEAM shows its superiority over TextCNN in all datasets in our experiments, by modeling labeling information.

LEAM does not perform as well as SFCs, since the first intuitive reason is it does not use a pretrained model as its input encoding module; 
another critical reason is in task-specific chat applications, it is common to have many similar intents, and it becomes hard and even impossible to name each intent with a short clear name to feed into LEAM model.
One candidate solution is setting a most standard sample as the label of the class. 
When using non-pretrained models base LEAM, this is applicable. 
Yet when using a pretrained model based, as all labels can be hundreds of thousands, then the training can not be accommodated in a poplar 32 G Tesla V100 GPU.

Actually, joint SFC can be kind of understood as a generalization form of LEAM. 
When there is no clear class labels, the relationship between a sample and a class label is implicitly encoded as that between a sample and another sample from the same class, and this turns into a sentence pair similarity model.

>>>>

\subsection{Datasets}
Our experiments aim to study the short text classification in the low-resource environment popular in the task-specific conversational chatbot application.
The datasets adopted in our experiments, showed in Table \ref{tbe:dataset statistic} \footnote{All settings of six public datasets would be released to github soon.}, typically contain comparatively large number of class labels, ranging from several dozens to hundreds, and each class label is associated with a handful of labeled queries with each query being usually one sentence.

@@

Our SFC implementations include three 2-stage SFCs using task 1 and 2 with ablation in Table \ref{tbe:table2}; one joint SFC trained on all three tasks in Table \ref{tbe:table2}; one joint SFC with an additional fourth NER task in Table \ref{tbe:addtional ner experiments}.

@@

\subsubsection*{Multi-task and joint training} 
\begin{table}
  \begin{centering}
    \scalebox{0.65}{
      \begin{tabular}{|c|ccc|ccc|}
        \hline
        \multicolumn{1}{|c|}{\multirow{2}*{\textbf{Models}} }& \multicolumn{3}{c|}{\textbf{FRAMES}}& \multicolumn{3}{c|}{\textbf{ATIS}}\tabularnewline
        \cline{2-7}
        \multicolumn{1}{|c|}{} & $\textbf{10}$ & $\textbf{20}$ & $\textbf{50}$
        & $\textbf{10}$ & $\textbf{20}$ & $\textbf{50}$\tabularnewline
        \hline
        RoBERTa-large & \multirow{2}*{${0.3456}$} & \multirow{2}*{${0.4043}$} & \multirow{2}*{${0.4262}$} & \multirow{2}*{${0.9349}$} & \multirow{2}*{${0.9757}$} & \multirow{2}*{${0.9800}$}\tabularnewline
        (classification) & & & & & & \tabularnewline
        \hline
        RoBERTa-large & \multirow{3}*{${0.3520}$} & \multirow{3}*{${0.4088}$} & \multirow{3}*{${0.4353}$} & \multirow{3}*{${0.9560}$} & \multirow{3}*{${0.9706}$} & \multirow{3}*{$\textbf{0.9832}$}\tabularnewline
        (classification & & & & & & \tabularnewline
        w/ NER) & & & & & & \tabularnewline
        \hline
        Joint SFC & \multirow{2}*{${0.3843}$} &
        \multirow{2}*{${0.4130}$} & \multirow{2}*{${0.4390}$} &
        \multirow{2}*{${0.9618}$} & \multirow{2}*{${0.9761}$} & 
        \multirow{2}*{${0.9825}$}\tabularnewline
        (w/o NER) & & & & & & \tabularnewline
        \hline
        Joint SFC & \multirow{2}*{$\textbf{0.3925}$} &
        \multirow{2}*{$\textbf{0.4420}$} & \multirow{2}*{$\textbf{0.4456}$} &
        \multirow{2}*{$\textbf{0.9639}$} & \multirow{2}*{$\textbf{0.9784}$} & 
        \multirow{2}*{${0.9826}$}\tabularnewline
        (w/ NER) & & & & & & \tabularnewline
        \hline
      \end{tabular}
    }
  \end{centering}

@@

\begin{table}
  \begin{centering}
    \scalebox{0.85}{
      \begin{tabular}{|c|c|c|c|}
        \hline
        F1 score & 2-stage SFC & joint SFC & Gap \tabularnewline
        \hline
        top-1 accuracy & \textbf{81.50} & 81.07 & -0.47 \tabularnewline
        top-5 accuracy & 94.01 & \textbf{94.30} & +0.29 \tabularnewline
        \hline
      \end{tabular}
    }
    \par
  \end{centering}
  \caption{The average classification accuracy in percentage in stage 1 on all five dataset.}
  \label{tbe:top1_5_accuracy}
\end{table}

@@

Joint SFC consistently outperforms 2-stage SFC with multi-task training on 5 diverse datasets by 0.95 percentage point on average. 
Though a joint model structure may bring extra complexity to the system, it does alleviate the error propagation from the first stage and improves the final performance.

In following analysis, we will focus on the comparison between joint SFC and the other baseline models.

\subsubsection*{Fusion of classification and similarity models} 
%We compare joint SFC with classification, similarity and NER joint model based baselines respectively.

\begin{table}
  \begin{centering}
    \scalebox{0.58}{
      \begin{tabular}{|c|c|c|c|c|c|c|}
        \hline 
        \multicolumn{1}{|c|}{\multirow{2}*{Dataset}}&\multicolumn{1}{c|}{\multirow{2}*{Model}}& $K=3$ & $K=5$ & $K=10$ & $K=15$ & $K=20$\tabularnewline
        \multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & $P=20$ & $P=10$ & $P=5$ & $P=4$ & $P=3$\tabularnewline
        \hline
        \multicolumn{1}{|c|}{\multirow{2}*{ITG}}& 2-stage SFC & $0.8034$ & $0.8124$ & $0.8008$ & $0.7967$ & $0.7934$\tabularnewline
        \cline{2-7}
        \multicolumn{1}{|c|}{} & joint SFC & $0.7986$ & $0.8114$ & $0.8010$ & $0.7972$ & $0.7918$\tabularnewline
        \hline
        \multicolumn{1}{|c|}{\multirow{2}*{Amazon-670k}}& 2-stage SFC & $0.7278$ & $0.7364$ & $0.7366$ & $0.7328$ & $0.7204$\tabularnewline
        \cline{2-7}
        \multicolumn{1}{|c|}{} & joint SFC & $0.7334$ & $0.7445$ & $0.7516$ & $0.7344$ & $0.7373$\tabularnewline
        \hline
      \end{tabular}
      \par
    }
  \end{centering}
  \caption{
    The performances of SFC from different settings of hyperparameters, $K$ denoting the candidate class number from stage 1,
    $P$ denoting the number of sampled sentence pair in stage 2. 
  }
  \label{tbe:table3}
\end{table}

Regarding the classification models, joint SFC outperforms RoBERTa-large based, the strongest among all baselines, by 2.04 percentage points on average F1 score over 5 datasets. 
Especially, ALBERT.xxlarge based is rather unstable in this short sentence task. 
Thus, we run multiple times with different settings and report the best ones here. 
Comparatively, RoBERTa based is the most stable and has the best performance almost all experiment settings.

Regarding the similarity model, as analyzed above, we only choose the RoBERTa-large based implementation as our baseline. 
Joint SFC achieves more improvement of 7.09 percentage points on average F1 score. 
This is also understandable, since RoBERTa-large based similarity model does not and also can not train towards the task specific goal.

@@

\subsubsection*{Joint SFC improves stage 1?}
We explore the quality of predicted candidate labels in stage 1 from 2-stage SFC and joint SFC respectively. 
We should note that 2-stage SFC does not optimize the stage 1 model, namely a RoBERTa based classification model.

From Table \ref{tbe:top1_5_accuracy}, the joint training does not improve the top-1 classification accuracy in stage 1, yet it improves the top-5 accuracy.
The reason is that, a classification model inherently optimizes the objective loss, 0-1 error of top-1 here; the sentence pair similarity model in joint SFC poses more positive effect in optimizing the candidate labels.

\subsubsection*{Supportive of extra NER task}
Many previous work shows joint training with a NER loss improves the intent classification task as well, observed again in our baselines and SFCs in Table \ref{tbe:addtional ner experiments}.
We choose the state-of-the-art RoBERTa-large model with NER loss as a strong baseline.

We can see that our joint SFC without NER loss still outperforms RoBERTa with NER loss baseline by 0.86 percentage points on average. 
This indicates that the fusion of classification and similarity models can even works better than fusing with additional NER information under few-shot chatbot scenario.

Moreover, the adding NER loss to joint SFC further achieves improvement of 1.66 percentage points over RoBERTa with NER loss baseline. 
Especially on FRAMES dataset, which is a much more difficult task in comparison with ATIS based on performance of all systems on it, our joint SFC with NER loss achieves a bigger improvement of 2.8 percentage points on average.

\subsubsection*{Different training sample size} 
We analyze the overall improvement trend of joint SFC under various few-shot settings, and show results in Fig. \ref{fig:trend}.

Our main focus is on studying chatbot construction in real world applications, where each class has only a small number of example sentences.
The experimental results for the 3 diverse intent detection datasets (ClINC150, BANKING77, HWU64) under few-shot settings, 5 to 50 samples per class, indicate that our proposed joint SFC can achieve average 2.47 percentage points improvement over one of the most powerful baseline models, which is RoBERTa-large classification model. 
Moreover, the improvement in F1 score becomes more and more prominent with the decrease of data sample number per class.

@@

Especially, in the most extreme setting with only 5 training samples per class, joint SFC achieves 4.97 percentage points improvements on average over RoBERTa-large classification model. 
Joint SFC is a better choice applied into the early stage of building a task-specific chatbot system, since label data is extremely scarce.

@@

\subsection{Settings of hyperparameters} 
In Table \ref{tbe:table3}, we explore the influence from hyperparameters on ITG and Amazon-670K datasets. 
We control the total number of sampled sentence pairs to about 50 to 60, and obatin about five combinations of hyperparameters.

We find that the best setting of hyperparameters is different with different datasets. 
The class label number of ITG and Amazon-670k are similar in our experiments, around 250. 
However the number of data points in ITG is approximately 2 times as many as that in Amazon-670k.
Therefore, the setting of $K=5$ and $P=10$ is good enough for ITG since most of the classes contains over 10 data points. 
However, in Amazon-670k, the data per each class is scarce, and, we may need more candidate classes to sample enough effective sentence pairs for the stage 2 traininig of SFC. 
Thus, the setting of $K=10$ and $P=5$ becomes a good choice.

However, despite the effect on evaluation performance brought by different settings of hyperparameters, joint SFC still steadily outperforms two-stage SFC by 0.41 percent points in overall average F1 score on ITG and Amazon-670k datasets.

For the experiments in Table \ref{tbe:table2}, we empirically set the hyperparameter to be $K=5$ and $P=10$ for all SFC variants.

\subsection{Other settings}
We fine-tune all SFC systems with the maximum sequence length of 128, learning rate of 1.5e-5 for RoBERTa-large pretrained model and 5e-4 for task-specific layer with a linear decay, and use Adam optimizer.

In two-stage SFC, in equ. \ref{eq:two-stage_SFC_loss} the weights of two tasks are set as $\alpha_S=0.125$ and $\alpha_K=0.875$ in our setting. 
In joint SFC, in equ. \ref{eq:joint_SFC_loss}, the weights of three tasks are set as $\alpha_S=0.25$, $\alpha_K=0.25$ and $\alpha_C=0.5$. 
Overall, the task weights are less sensitive in joint SFC than in two-stage SFC.

As for the training time, in our settings, our joint SFC model needs about 14 hours to reach convergence using a single Nvidia RTX8000 GPU. 
In comparison, the classification baseline model needs about 5 hours and the similarity baseline model needs about 12 hours.

### 2021-05-18 chatbot_classification/03.emnlp_2021/methodology.tex
modified:   experiments.tex   modified:   methodology.tex

The size of ${\Phi}^S$ in task 1, namely unnormalized probabilistic distribution, is $2 \times M$, as $M$ sentence pairs corresponds two class labels.
Further, it equals $(N\cdot K\cdot P)\times 2$, where $N$ is the total number of data points in original training data $\mathcal{D}$, $K$ is a hyperparameter that controls the number
of candidate class labels provided by stage 1, and $P$ is also a hyperparameter that controls the number of sentences we should randomly sample from each candidate class labels. 
Now, for the average pooling layer, we first reshape ${\Phi}^S$ into the size of $N\times K\times P\times 2$, and then split it into ${\Phi}^{K,pos}$ and ${\Phi}^{K,neg}$, and both of them will have the size of $N\times K\times P$. 
In this way, ${\Phi}^{K,pos}$ represents the level of similarity for each sentence pair, and ${\Phi}^{K,neg}$ represents the level of dissimilarity for each sentence pair. 
Then, we can do average pooling for each candidate class among the top-K classes as shown in Equ. \ref{eq:average pooling}.

@@

        \multirow{2}*{Joint-SFC} & \multirow{2}*{$\textbf{0.9231}$} & \multirow{2}*{$\textbf{0.9560}$} & \multirow{2}*{$\textbf{0.9644}$} & \multirow{2}*{$\textbf{0.9669}$} & \multirow{2}*{$\textbf{0.9712}$} & \multirow{2}*{$\textbf{0.9821}$} & \multirow{2}*{$\textbf{0.8270}$} & \multirow{2}*{$\textbf{0.9069}$} & \multirow{2}*{$\textbf{0.9103}$} & \multirow{2}*{$\textbf{0.9209}$} & \multirow{2}*{$\textbf{0.9323}$} & \multirow{2}*{$\textbf{0.9463}$} & \multirow{2}*{$\textbf{0.6697}$} & \multirow{2}*{$\textbf{0.7211}$} & \multirow{2}*{$\textbf{0.7254}$} & \multirow{2}*{$\textbf{0.7497}$} & \multirow{2}*{$\textbf{0.7593}$} & \multirow{2}*{$\textbf{0.7772}$} & \multirow{2}*{$0.8114$} & \multirow{2}*{$\textbf{0.7445}$}\tabularnewline

@@

\subsection{Joint SFC}
In 2-stage SFC, Stage 1 and stage 2 are separate that there is no deep
interaction with each other during training. In this case, the performance of
stage 1 may limit the potential of stage 2; meanwhile, stage 2 also cannot
give training feedback back to stage 1 for fine-tuning. Therefore, to further
improve the overall performance of SFC, we proposed a joint model structure,
shown in Fig. \ref{fig:framework}.

In joint-SFC, classification model is being placed in lower layer level to
dynamically provide top-K candidate class labels for the sentence-pair
similarity model placed in higher layer level through a top-K pooling layer.
In this way, classification model and similarity model can be merged into one
single joint-model for multi-task training with sentence pairs sampled from
varying candidate class labels, thus avoiding the limitation brought by 2
separate stage structure.

There are 3 tasks in total during the training process of joint-SFC, shown in
Fig. \ref{fig:framework}, and the overall loss is also the weighted sum of all
the task-specific losses, shown in Equ. \ref{eq:joint_SFC_loss}. Here,
$\alpha_S$, $\alpha_K$ and $\alpha_C$ represent the weights for task 1
sentence-pair similarity in Equ. \ref{eq:similarity_loss}, task 2 top-K
classification in Equ. \ref{eq:top-k_classification_loss}, and task 3 general
single sentence classification respectively in Equ.
\ref{eq:classification_loss}.

>>>>

The size of ${\Phi}^S$ in task 1, namely unnormalized probabilistic distribution, is $2 \times M$, as one sentence pair correspond to two class labels.
Further, it equals $(N\cdot K\cdot P)\times 2$, where $N$ is the size of original training data $\mathcal{D}$, $K$ the number of candidate class labels from stage 1, and $P$ is the number of sentences randomly sampled from each candidate class label. 
Now, for the average pooling layer, we first reshape ${\Phi}^S$ into the size of $N\times K\times P\times 2$, and then split it into ${\Phi}^{K,pos}$ and ${\Phi}^{K,neg}$, and both of them will have the size of $N\times K\times P$. 
In this way, ${\Phi}^{K,pos}$ represents the level of similarity for each sentence pair, and ${\Phi}^{K,neg}$ represents the level of dissimilarity for each sentence pair. 
Then, we can do average pooling for each candidate class among the top-K classes as shown in Equ. \ref{eq:average pooling}.

@@

        \multirow{2}*{Joint SFC} & \multirow{2}*{$\textbf{0.9231}$} & \multirow{2}*{$\textbf{0.9560}$} & \multirow{2}*{$\textbf{0.9644}$} & \multirow{2}*{$\textbf{0.9669}$} & \multirow{2}*{$\textbf{0.9712}$} & \multirow{2}*{$\textbf{0.9821}$} & \multirow{2}*{$\textbf{0.8270}$} & \multirow{2}*{$\textbf{0.9069}$} & \multirow{2}*{$\textbf{0.9103}$} & \multirow{2}*{$\textbf{0.9209}$} & \multirow{2}*{$\textbf{0.9323}$} & \multirow{2}*{$\textbf{0.9463}$} & \multirow{2}*{$\textbf{0.6697}$} & \multirow{2}*{$\textbf{0.7211}$} & \multirow{2}*{$\textbf{0.7254}$} & \multirow{2}*{$\textbf{0.7497}$} & \multirow{2}*{$\textbf{0.7593}$} & \multirow{2}*{$\textbf{0.7772}$} & \multirow{2}*{$0.8114$} & \multirow{2}*{$\textbf{0.7445}$}\tabularnewline

@@

\subsection{Joint SFC}
In 2-stage SFC, two stages are separate that there is no deep interaction with each other during training. 
In this case, the performance of stage 1 may limit the model potential in stage 2; 
meanwhile, stage 2 also cannot loop feedback back to stage 1 in trainig for improvement. 
Therefore, we propose to jointly train all stages, shown in Fig. \ref{fig:framework}.

In joint SFC, a classification model is placed in stage 1 to dynamically provide top-K candidate class labels for the sentence-pair similarity model in stage 2 through a top-K pooling layer.
In this way, classification model and similarity model can be merged into one single model for multi-task training with sentence pairs sampled from varying candidate class labels.

There are 3 tasks in total during the training of joint SFC, shown in Fig. \ref{fig:framework}. 
The overall loss is a linear combination of them, shown in Equ. \ref{eq:joint_SFC_loss}. 
Here, $\alpha_S$, $\alpha_K$ and $\alpha_C$ represent the weights for task 1 sentence-pair similarity in Equ. \ref{eq:similarity_loss}, task 2 top-K classification in Equ. \ref{eq:top-k_classification_loss}, and task 3 general single sentence classification respectively in Equ.  \ref{eq:classification_loss}.
